---
title       : Finding Anomalies with K-means
subtitle    : With Shiny
author      : Kyle
job         : 
framework   : html5slides        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : #selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Anomaly Detection

- At work I anaylize software system data
- Most of it isn't interesting, but occasionally something abnormal happens
- My goal is to find out when that happens and why
- To do this I look for anomalies

```{r,echo=FALSE,fig.align='center',fig.height=3.9}
x <- rnorm(100,mean=5,sd=1)
x[1] <- x[1]+5
y <- rnorm(100,mean=5,sd=1)
y[1] <- y[1]+5
plot(x[2:100],y[2:100],col="blue",main="Anomaly",xlab="X",ylab="Y",
     xlim = c(1,12),ylim=c(1,12),pch=3)
points(x=x[1],y=y[1],col="red",pch=7)

```

--- .class #1

## How to find Anomalies in Data 
- There are a couple ways to find them
1. Density
2. Distance
3. Statistical Properties

Density  | Distance | Statistical
---------| ---------|------------
LOF      | Kmeans   | Parametric Models
CBOF     | Knn      | Mean, Var, Stdev
DENLCUE  | LDOF     | Distribution Assumptions

--- .class #2


## Don't Fear!

- Building some of the models mentioned is difficult
- Luckily R has many models already made
- Kmeans is an example
- Caret also has a ton of built in functions for ML and Anomaly Detection

--- .class #3

## I'll help you get started

- https://kgartrell.shinyapps.io/Finding_Anomalies/
- That link goes to a shiny app that highlights Anomalies using Kmeans

--- .class #4

## Hopefully You Found This Interesting!

- Good luck coming up with your own algorithms

```{r}
2+2
```

### Kindest Regards,
### Kyle

--- .class #5

